 

### 2023-02-22 paper3.Rmd
Revising tables to improve readability
Addition of appendices, revisions throughout papers, acknowledgements

```{r loading, include=FALSE}

source("C:/Users/danie/Dropbox (Harvard University)/mh_scm/code/0_prep_file.R")

@@

load(file = paste(resultspath, "1_data",
                  "model_outputs_all_main.Rdata", sep = "/"))

load(file = paste(resultspath, "1_data",
                  "model_outputs_all_US.Rdata", sep = "/"))

load(file = paste(resultspath, "1_data",
                  "model_outputs_all_international.Rdata", sep = "/"))

load(file = paste(resultspath, "1_data",
                  "model_outputs_all_diseases.Rdata", sep = "/"))

@@

model_output_main <- model_outputs_all_US %>%
  function_model_main()

@@

  data %>%
    mutate(disease = str_to_sentence(str_replace_all(disease, "_", " "))) %>%
    mutate(disease = ifelse(disease == "Attention deficit hyperactivity disorder", "ADHD", disease),
           disease = ifelse(disease == "Generalized anxiety disorder", "GAD", disease),
           disease = ifelse(disease == "Major depressive disorder", "MDD", disease),
           disease = ifelse(disease == "Avoidant personality disorder", "AvPD", disease))

@@

list_diseases_all <- read.xlsx(paste(datapath, 
                         "list_of_diseases.xlsx", sep = "/")) %>%
  filter(mh_indicator == 1) %>%
  select(search)

list_diseases_all <- list_diseases_all$search

@@

@@

We take as our first credible signal of the imminent availability of safe and effective COVID-19 vaccines to be November 16, 2020. On November 9, Pzifer announced than early vaccine trial data showed 90% efficacy;[@thomasPfizerEarlyData2020] on the 16th, Moderna similarly announced preliminary results showing 94.5% efficacy for their vaccine.[@gradyEarlyDataShow2020] While U.S. Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners and laypersons as a substantial signal of a new phase of the pandemic, with Moderna's chief executive officer calling the news "a game changer" in the fight against COVID-19.

@@

We access U.S. county- and state-level data from Google’s COVID-19 Search Trends Symptoms Dataset[@Wahltinez2020](hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021 for six symptoms: anxiety, depression, generalized anxiety disorders, headache, major depressive disorders, and panic attacks. Data on headaches was obtained to provide a control trend from a common health symptom with comparative characteristics to mental health complaints.

* Linear interpolation to replace missing values
* Also used smoothing to address outliers (sensitivity analysis showed no difference when unadjusted values were used)
* Not all counties reported data (due to data privacy concerns, smaller county results were not included in the symptoms dataset)

@@

We further obtained county-level presidential election returns for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which we then used to calculate aggregate county and state votes (including absentee, early, and election day ballots) won by each candidate. The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the candidate with the most votes to the runner up); margins were then used to sort counties and states into quintiles, with the 20% most Republican-voting localities appearing in the symptoms dataset sorted into bin 1 and the 20% most Democratic-voting localities sorted into bin 5.

* Joined to symptoms dataset by FIPS code

## Statistical analysis

@@

### Modeling approach

We use a controlled interrupted time series (CITS) approach.

Model equation for Google search density (measured as the ratio between the normalized search volume for a given symptom during a given week and the median search volume for that symptom between 2018 and 2020):

$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_i + \lambda_3 time_t*Post_i + $$
$$ \alpha_d treated_{di} + \beta_d time_t*treated_{di} + \delta_{d} Post_i*treated_{di} + \gamma_d time_t*Post_i*treated_{di} + \epsilon_{it}$$
where $time_t$: is a continuous variable that captures the days leading to the vaccine announcement, $Post_i$: is an indicator variable which equals 1 in the "post" period and 0 otherwise, and $treated_di$: is an indicator variable which equals 1 if the observation is for a mental health condition $d$, 0 if for headaches.

The CITS effect estimates of interest are given by $\delta$, which reflects the additional level shift among mental health related symptoms searches compared to searches for headaches after the vaccine announcement, and  $\gamma$, the additional change in search density over time (i.e., slope change) comparing the same.

* Fixed effects included for day of week, month, and state
* Trim bandwidth to 40 days before and after the announcement
* Subgroup analysis by polity to examine whether effects were different in very Democrat leaning geographies vs. Republican leaning ones

### Sensitivity analysis

Interacted modeling decisions:

* County vs. state level aggregated data
* Replacement of outliers with smoothing
* Fixed effects for day of week
* Fixed effects for month
* Fixed effects for state
* Bandwidth selection (30, 40, 50, 60 days)

128 models for each disease and polity level (384 models per disease, 2,304 in total across all 6 conditions)

### Ethics statement
The Institutional Review Board (IRB) of the Harvard T.H. Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB23-0095, determined on January 25, 2023).

@@

* Sharp declines in searches for depression and anxiety following vaccine announcement
* No meaningful differences in searches for major depression and major anxiety, panic attacks, or sleep disorders
* Results do not strongly vary by polity

```{r figure_cits_outputs, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7, fig.height = 8, fig.align='center', out.width = '95%', fig.scap="Controlled interrupted time series effect estimates on Google Search density by symptom.", out.extra='',  fig.cap="\\label{figure_cits_outputs}Controlled interrupted time series effect estimates (A: slope change per 10 days and B: level shift)  on Google Search density by symptom. Effect estimates are represented as thick, horizontal lines in between colored bands, which represent the 99\\% confidence intervals for the estimates. Colors reflect the sign and magnitude of effect estimates. Dark blue values above zero indicate an increase in search density, while the yellow and green negative values indicate a decrease. The dotted horizontal line depicts a null effect. ADHD: Attention deficit hyperactivity disorder. GAD: Generalized anxiety disorder. MDD: Major depressive disorder."}

model_outputs_all_main %>% 
   function_model_main("exclude") %>%
  function_clean_diseases () %>%
  arrange(disease) %>%
   mutate(estimate = ifelse(coefficient == "post:time:trt", estimate*10, estimate),
         lower_99 = ifelse(coefficient == "post:time:trt", lower_99*10, lower_99),
         upper_99 = ifelse(coefficient == "post:time:trt", upper_99*10, upper_99)
         ) %>%
    mutate(coefficient = ifelse(coefficient == "post:time:trt", "A: slope change (per 10 days)",
                              ifelse(coefficient == "post:trt", "B: level shift", "ERROR"))) %>%
  mutate(sign = ifelse(estimate >0, TRUE, FALSE)) %>%

model_outputs_all_diseases_graph <- model_outputs_all_diseases %>%
  mutate(coefficient = ifelse(coefficient == "post:time", "slope",
                              ifelse(coefficient == "post", "level", "ERROR"))) %>%
  select(coefficient, estimate, lower_95, upper_95, disease, p_value) %>%
  pivot_wider(names_from = coefficient,
              values_from = c(estimate, lower_95, upper_95, p_value)) %>%
  mutate(mh_indicator = ifelse(disease %in% list_diseases_all, 
                               "Mental symptom",
                               "Physical symptom"))  %>%
      function_clean_diseases()

model_outputs_all_diseases_graph %>%
  ggplot(aes(y = estimate_level, x = estimate_slope, color = mh_indicator, label = disease)) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0) +
  geom_errorbarh(aes(xmin = lower_95_slope, xmax = upper_95_slope), alpha = 0.3) +
  geom_errorbar(aes(ymin = lower_95_level, ymax = upper_95_level), alpha = 0.3) +
  theme_classic() +
  geom_point(alpha = 0.75) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size=12),

    text = element_text(family = "Source Sans Pro")) +
      scale_color_manual(values = c(col_mh,
                                    col_grey_lightest),
                         name = "") +
      labs(x = "Slope change", y = "Level shift") +
  geom_text_repel(data=subset(model_outputs_all_diseases_graph, estimate_slope < -0.04 |
                                (estimate_slope <.01 & mh_indicator ==  "Mental symptom")),
                  size = 3)

```{r figures_cits_data, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 9.5, fig.height = 8, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends, by symptom and region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data}Density of Google Search trends, by symptom and region, as a function of time. In each row, search density data for two symptoms are displayed: one of three mental health symptoms (from top to bottom: anxiety, depression, and major depressive disorder) in blue and headaches in grey. In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state. In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots. In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown. Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis. The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects). US: United States."}

@@

for (m in mental_disorders) {
  for (g in geography){
    data_its <- get(paste0("data_its_",g))

@@

  }
}

    combo_plot_1 <- cowplot::plot_grid(plot_1,
                                       plot_2,
                                      plot_3,
                                      plot_4,
                                       plot_5,
                                      plot_6,
                                      plot_7,
                                       plot_8,
                                      plot_9,
                       align='v', ncol=3, axis='b')

    print(combo_plot_1)

@@

>>>>

```{r loading, include=FALSE}
  # Loading libraries
  library(readxl)
  library(readr)
  library(dplyr)
  library(zoo)
  library(tidyr)
  library(psych)
  library(ggplot2)
  library(RColorBrewer)
  library(sp)
  library(broom)
  library(sf)
  library(scales)
  library(viridis)
  library(data.table)
  library(ggpubr)
  library(ggmap)
  library(maps)
  library(mapdata)
  library(ggrepel)
  library(table1)
  library(stringr) 
  library(stringi)
  library(fixest)
  library(stats)
  library(lubridate)
  library(forecast)
  library(gtools)
  library(stargazer)
  library(lwgeom)
  library(openxlsx)
  library(gganimate)
  library(transformr)
  library(huxtable)
  library(ggtext)
  library(magrittr)
  library(lmtest)
  library(sandwich)
  library(rgee)
  library(gt)
  library(knitr)
  library(webshot2)
  library(sysfonts)
  library(showtext)
  font_add_google("Source Sans Pro")
  library(gridExtra)
  library(tibble)
  showtext_auto() 
  showtext_opts(dpi = 300)  
  library(augsynth)
  library(dvmisc)
  library(forcats)
  library(rmdHelpers)

  # Setting directories - change these to your local directory
  path <- 'C:/Users/danie/Dropbox (Harvard University)/mh_scm'

  codepath <- paste(path,'code', sep = "/")

  # Github. Ask golden@hsph.harvard.edu for access. 
  datapath <- paste(path,'data', sep = "/")

  # Results
  resultspath <- paste(path,'results', sep = "/")

  # Shapefiles
  mappath <- paste(path,'shapefiles', sep = "/")

  # Color palette 
  col_light = "cyan4"
  col_dark = "cyan3"
  col_bright = "coral"
  col_black = "black"
  col_grey_dark = "grey20"
  col_grey_med = "grey40"
  col_grey_light = "grey80"
  col_grey_lightest = "grey85"
  col_soilmoisture = col_dark
  col_temperature = col_light
  col_interaction = col_bright
  col_mh = "steelblue3"
  col_headache = "grey50"

  col_model_main <- "#F3AB00"
  col_model_other <- col_grey_med
  col_spec_yes <-  "#73BDBF"
  col_spec_no <-  "white"

  col_positive <- "salmon1"
  col_negative <-"steelblue2"

  col_all <- "plum3"
  col_dem <- "steelblue2"
  col_red <- "red2"

  # Seed 
  set.seed(4800)

  ######################
  ##      DATES        ##
  ######################

  date_shock_vax <- as.Date("2020-11-16")
  trim_bandwidth = 60

  start_date <-  date_shock_vax -  trim_bandwidth  #as.Date("2020-06-01")
  end_date <- date_shock_vax + trim_bandwidth  #as.Date("2021-05-31")

  disorders <- c("anxiety", "depression", "fever", "generalized_anxiety_disorder",
                 "hair_loss", "headache", "major_depressive_disorder",
                 "pain","panic_attack","sleep_disorder")

  week_shock_vax <- floor(as.numeric((date_shock_vax - start_date) / 7))

@@

load(file = paste(resultspath, "1_data",
                  "model_outputs_main.Rdata", sep = "/"))

load(file = paste(resultspath, "1_data",
                  "model_outputs_political.Rdata", sep = "/"))

load(file = paste(resultspath, "1_data",
                  "model_outputs_multiverse.Rdata", sep = "/"))

load(file = paste(resultspath, "1_data",
                  "model_outputs_international.Rdata", sep = "/"))

load(file = paste(resultspath, "1_data",
                  "model_outputs_its.Rdata", sep = "/"))

@@

model_output_main <- model_outputs_political %>%
  function_model_main()

@@

  data %>%
    mutate(disease = str_to_sentence(str_replace_all(disease, "_", " "))) %>%
    mutate(disease = ifelse(disease == "Attention deficit hyperactivity disorder", "ADHD", disease),
           disease = ifelse(disease == "Clouding of consciousness", "CoC", disease),
           disease = ifelse(disease == "Generalized anxiety disorder", "GAD", disease),
           disease = ifelse(disease == "Major depressive disorder", "MDD", disease),
           disease = ifelse(disease == "Avoidant personality disorder", "AvPD", disease))

@@

list_mental_health_symptoms <- read.xlsx(paste(datapath, 
                                               "list_of_diseases.xlsx", sep = "/")) %>%
  filter(mh_indicator == 1) %>%
  select(search)

list_mental_health_symptoms <- list_mental_health_symptoms$search

@@

controlled interrupted time series (CITS) 
interrupted time series (ITS)

@@

We take as our first credible signal of the imminent availability of multiple safe and effective COVID-19 vaccines to be November 16, 2020. On November 9, Pzifer announced than early vaccine trial data showed 90% efficacy;[@thomasPfizerEarlyData2020] on the 16th, Moderna similarly announced preliminary results showing 94.5% efficacy for their vaccine.[@gradyEarlyDataShow2020] While U.S. Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.

@@

We accessed aggregated national and subnational data from Google’s COVID-19 Search Trends
Symptoms Dataset [@Wahltinez2020] (hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021. The symptoms dataset provides time series data of search term density, standardized to pairs of health symptoms and regions (e.g., searches for depression in Australia or for fever in Cook County, Illinois) and normalized within each pair based on the symptom’s relative popularity. The time series of search density for each symptom-region pair also contains artificial noise, as Google’s differential privacy technique to data aggregation and anonymization adds random noise to protect user privacy (the errors are symmetrically distributed).

Search density data for over 400 symptoms are reported across national and subnational regions of six countries: Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States. In the United States, subnational regions include states and counties.  Because the aggregated search density trends were constructed based on relative search population within each region, comparison of search density for a specific symptom between different regions is not meaningful; however, comparing search density within regions (or a group of regions) is feasible both over time and across different symptoms.

```{r methods_text_1}

n_states <- data_its_state %>% select(state_name) %>% unique() %>% nrow()
n_counties <- data_its_county %>% select(county_fips) %>% unique() %>% nrow()

n_states <- format(n_states, big.mark = ",")

n_counties <- format(n_counties, big.mark = ",")

For our analysis, we utilized three levels of region from the symptoms dataset: 1) national level data from the six countries in the dataset; 2) U.S. state level data across `r n_states` states; and 3) U.S. county level data reported by `r n_counties` counties. (Though there are over 3,000 counties in the U.S., due to data privacy concerns, smaller county results were not included in the symptoms dataset.) Following the convention of the symptoms dataset, we will refer to the geographic units (e.g., states, counties, and nations) within the data as "regions."

@@

We further obtained county-level presidential election returns for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which we then used to calculate aggregate county and state votes (including absentee, early, and election day ballots) won by each candidate. The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the candidate with the most votes to the runner up). These margins were then used to sort counties and states into quintiles, such that the 20% most Republican-voting localities appearing in the symptoms dataset were sorted into the first quintile and the 20% most Democratic-voting localities sorted into the fifth).

#### Population data

Population estimates for 2020 by Federal Information Processing Standards (FIPS) code were obtained from the United States Department of Agriculture (USDA) Economic Research Service.

### Statistical analysis

@@

#### Modeling approach

We use an ITS approach to model Google search density for a given symptom $d$ using the following baseline equation: $$Y_{d,g, i} = \lambda_0 + \lambda_1 time_t + \alpha_d Post_{d,i} + \beta_d time_t*post_{d,i} + \theta_r + T^{'}_t\chi + \epsilon_{it} \ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)$$ where $time_t$ is a continuous variable that captures the days leading to the vaccine announcement, $Post_i$ is an indicator variable which equals 1 in the period after the shock data and 0 otherwise, $\theta_r$ is a fixed effect for region $r$, and $T^{'}_t\chi$ is a matrix of time-vary fixed effects (i.e., month and day of week).

In our model, $\alpha_d$ can be interpreted as a level or intercept associated with the shock date—that is, the immediate difference in search density for a disease $d$ following November 19, 2020. The term $\beta_d$—i.e., the slope change—can be interpreted as the sustained change in search density in the days following November 16th.

```{r methods_text}

diseases_n <- format(max(model_outputs_its$model_number), big.mark = ",")  
mh_diseases_n <- format(length(list_mental_health_symptoms), big.mark = ",")  
num_models_multiverse = format(max(model_outputs_multiverse$model_number), big.mark = ",")

```
We apply this model for all available `r diseases_n` diseases with county-level data. As search density may rapidly change in response to a shock, we trimmed the bandwidth of dates to fit our model to forty days before and after November 16, 2020.

To control for time-varying confounders which may have affected symptom search trends during the study period, we applied a CITS approach to contrast how searches for mental health symptoms varied above and beyond changes in search density for a comparable physical complaint (i.e., headaches).

After reviewing the list of symptoms for which search density data were available, we identified the following `r mh_diseases_n` mental health related symptoms: `r paste0(gsub("asperger", "Asperger", gsub("_", " ", printList(toPrint = sort(list_mental_health_symptoms), finalSepWord = "and", midSep = ","))),".")`

For each of these mental health symptoms, $d$, we ran the following model to predict search density:

\begin{spacing}{1}

$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_t + \lambda_3 time_t*Post_t + \alpha_d treated_{di} + 
\ \ \ \ \ $$
$$\beta_d time_t*treated_{di}  + \delta_{d} Post_i*treated_{di} + \gamma_d time_t*Post_i*treated_{di} + \theta_g + T^{'}_t\chi +  \epsilon_{it}\ \ \ ,\ \ \ \ \ \ \ \ \ \ (3.2)$$
\end{spacing}

\vspace{12pt}

where $treated_{di}$: is an indicator variable which equals 1 if the observation is for a mental health condition $d$, 0 if for headaches. The CITS effect estimates of interest are given by $\delta$, which reflects the additional level shift among mental health related symptoms searches compared to searches for headaches after the vaccine announcement, and  $\gamma$, the additional change in search density over time (i.e., slope change) comparing the same.

Given the high number of observations in our sample, we evaluated significance against an alpha of 0.01, and we constructed 99% confidence intervals using heteroskedasticity-robust standard errors.

##### Sensitivity analysis

As with other quasi-experimental methods, it is recommended that the modeling choices and specifications of a CITS analysis be evaluated using a sensitivity analysis. To do so, we defined a list of seven methodological choices concerning data processing and modeling assumptions and interacted these choices to generate all their plausible  combinations. These combinations were then conducted to allow for a multiverse analysis to identify how sensitive effect estimates and confidence intervals were to different methodological choices.

These criteria used to generate the plausible model combinations are outlined in Table 3.1.

\vspace{12pt}

```{r table3_1, echo = FALSE, include = TRUE, out.width = '100%'}

knitr::include_graphics("table3_1.png")

\addcontentsline{lot}{table}{Table 3.1: Alternative specifications, data processing, and modeling decisions for multiverse analysis}

First, we considered the role of data cleaning in the outcome data, which involved outlier smoothing using Friedman’s nonparametric super smoother regression estimator.[@friedmanVariableSpanScatterplot1984] Second, we compared the level of region of aggregated data, using U.S. counties, U.S. states, and, finally, national trends from the six counties in the sample. Third, we evaluated sensitivity to our specification of the bandwidth cut-off around the shock date, extending this from ±40 days to 40 and 60 days. Fourth, we toggled whether to account for day of week fixed effects. Fifth, we toggled month fixed effects. Sixth, we similarly toggled regional fixed effects (i.e., fixed effects for states in the U.S. state level data, fixed effects for counties in the U.S. county level data, etc.).

Interacting these choices resulted in 144 plausible models for each symptom. Each of the 144 models were run for all `r mh_diseases_n` mental health related symptoms, resulting in `r num_models_multiverse` models being conducted overall.

##### Subgroup analysis

Two subgroup analyses were conducted to investigate the generalizability of the findings of the main analysis and to explore potential heterogeneities in measures of association.

The first subgroup analysis applied the CITS approach against all `r mh_diseases_n` mental health related symptoms against search data from each of the six countries in the sample, using our nationally aggregated data. This analysis aimed to investigate the extent to which effects observed in US states and counties were also seen in other countries.

The second subgroup analysis applied the CITS approach to the 20% most Republican-voting localities (hereafter referred to as red states/counties) and to the 20% most Democratic-voting localities (hereafter referred to as blue states/counties) based on 2020 presidential election vote share. A growing body of evidence has documented that political ideology can play a role in how receptive people are to vaccination; this has been highlighted throughout the COVID-19 pandemic, with people identifying as conservative being more likely to express skepticism of public health authorities and the scientific community and being more likely to express concerns about the safety, effectiveness, or necessity of vaccines. Our subgroup analysis comparing CITS effect estimates in blue vs. red states aimed to investigate whether the initial response to imminent safe and effective COVID-19 vaccines showed evidence of heterogeneity by predominant political ideology, under the hypothesis that if conservative voters were more likely to be averse to vaccination, any impact on mental health related symptom search density from the announcement of upcoming vaccines would be lesser in red states and counties compared to blue ones.

### Ethics statement

The Institutional Review Board (IRB) of the Harvard T.H. Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB23-0095, determined on January 25, 2023).

@@

function_dynamic_text_results <-
  function(section = "its",         #c(its, main, international, polity, multiverse)
           disease_option,
           coefficient_option,
           lag_option,
           region_option = "all",
           geography_option = "county",
           value_include = TRUE,
           multiverse_sign = "positive",
           multiverse_p = FALSE) #(TRUE, FALSE, only),)

  {output_df <- get(paste0(
    "model_outputs_",section))

  term <- ifelse(section == "its" & coefficient_option == "intercept",
                 "post", 
                 ifelse(section != "its" & coefficient_option == "intercept",
                        "post:trt",
                        ifelse(section == "its" & coefficient_option == "slope",
                               "post:time", "post:time:trt")))

  if(section == "multiverse"){

    if(multiverse_sign == "positive"){

      output_df <- output_df %>% filter(estimate >= 0)  %>% 
        filter(coefficient == term) %>%   
        filter(disease == disease_option)

    } else {output_df <- output_df %>% filter(estimate < 0)   %>% 
      filter(coefficient == term) %>%   
      filter(disease == disease_option)}

    if(multiverse_p != FALSE)
    {
      models_counts <- output_df <- output_df %>% filter(p_value < multiverse_p) %>% nrow()
      return(models_counts)

    } else {

      models_counts <- output_df %>% nrow()

      return(models_counts)

  }else{

    output_df <-
      output_df %>% filter(coefficient == term) %>%
      filter(disease == disease_option)

     if(section == "political"){ output_df <- output_df %>% filter(polity == region_option) %>%
       filter(geography == geography_option)}

    val <- round((output_df$estimate), 3)
    p_val <- round(output_df$p_value, 3)
    low <- round((output_df$lower_99), 3)
    high <- round((output_df$upper_99), 3)

    if (value_include == TRUE){

      return(paste0(
        val,
        " percentage points",
        ifelse(coefficient_option == "slope",
               " per day "," "),
        "(p ",
        ifelse(p_val < 0.001,
               "< 0.0001, ",
               paste0("= ",
                      p_val,
                      ", ")),
        "99\\% CI: ",
        low,
        " – ",
        high
        ,
        ")"))

    if (value_include == "allnumber"){

      return(paste0(
        "(",
        val,
        ", p ",
        ifelse(p_val < 0.001,
               "< 0.0001, ",
               paste0("= ",
                      p_val,
                      ", ")),
        "99\\% CI: ",
        low,
        " – ",
        high
        ,
        ")"))

    if (value_include == FALSE){

      return(paste0(
        "(p ",
        ifelse(p_val < 0.001,
               "< 0.0001, ",
               paste0("= ",
                      p_val,
                      ", ")),
        "99\\% CI: ",
        low,
        " – ",
        high
        ,
        ")"))

    if (value_include == "only"){
      # Estimate only

      return(val)

function_pval_stars <- function(x){

  ifelse(stars.pval(x) ==".", "", stars.pval(x))

function_figures_cits_data <- function(geography,m){

@@

  for (g in geography){

    data_its <- get(paste0("data_its_",g))

@@

  combo_plot_1 <- cowplot::plot_grid(plot_1,
                                   plot_2,
                                   plot_3,
                                   # plot_4,
                                   # plot_5,
                                   # plot_6,
                                   # plot_7,
                                   # plot_8,
                                   # plot_9,
                                   align='v', ncol=1, axis='b') 
 print(combo_plot_1)

@@

The ITS estimates for the immediate (level shift) and sustained (slope change) effects associated with the announcement of vaccine safety and efficacy data on search density for all `r diseases_n` are presented in Figure \ref{figure_all_diseases}.

For most symptoms, search density exhibited negligible differences following the announcement, with small positive level shifts offset by modest negative slope changes. For four mental health symptoms, however, we observed relatively large, negative slope changes for searches for anxiety `r function_dynamic_text_results("its","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("its","depression", "slope", value_include = "allnumber")`, major depressive disorder (MDD)`r function_dynamic_text_results("its","major_depressive_disorder", "slope", value_include = "allnumber")`, and attention deficit hyperactivity disorder (ADHD)`r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "slope", value_include = "allnumber")`. With respect to level shifts, changes for anxiety `r function_dynamic_text_results("its","anxiety", "intercept", value_include = "allnumber")` and depression `r function_dynamic_text_results("its","depression", "intercept", value_include = "allnumber")` were close to zero, while those for MDD `r function_dynamic_text_results("its","major_depressive_disorder", "intercept", value_include = "allnumber")` and ADHD `r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "intercept", value_include = "allnumber")` were approximately 0.3 percentage points.

model_outputs_its_graph <- model_outputs_its %>%
  mutate(coefficient = ifelse(coefficient == "post:time", "slope",
                              ifelse(coefficient == "post", "level", "ERROR"))) %>%
  select(coefficient, estimate, lower_95, upper_95, disease, p_value) %>%
  pivot_wider(names_from = coefficient,
              values_from = c(estimate, lower_95, upper_95, p_value)) %>%
  mutate(mh_indicator = ifelse(disease %in% list_mental_health_symptoms, 
                               "Mental symptom",
                               ifelse(disease == "headache", 
                                      "Headache (control)",
                                      "Physical symptom")))  %>%
  mutate(mh_indicator = factor(mh_indicator, 
                               levels = c("Mental symptom", 
                                          "Headache (control)",
                                          "Physical symptom"))) %>%
  function_clean_diseases()

model_outputs_its_graph %>%
  ggplot(aes(y = estimate_level, x = estimate_slope, color = mh_indicator, label = disease)) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0) +
  geom_errorbarh(aes(xmin = lower_95_slope, xmax = upper_95_slope), alpha = 0.3) +
  geom_errorbar(aes(ymin = lower_95_level, ymax = upper_95_level), alpha = 0.3) +
  theme_classic() +
  geom_point(alpha = 0.75) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size=12),

    text = element_text(family = "Source Sans Pro")) +
  scale_color_manual(values = c(col_mh,
                                col_headache,
                                col_grey_lightest),
                     name = "") +
  labs(x = "Slope change", y = "Level shift") +
  geom_text_repel(data=subset(model_outputs_its_graph, estimate_slope < -0.04 |
                                (estimate_level <.1 & mh_indicator ==  "Mental symptom" |
                                   mh_indicator == "Headache (control)")), max.overlaps = 10,
                  size = 3)

While our ITS analysis provided suggestive evidence that search density for mental health symptoms might have changed in the post-announcement period, it also highlighted that searches may have generally changed across other diseases at the same time. Our CITS estimates of each mental health symptom (Figure \ref{figure_cits_outputs}) using searches for headaches as a comparison broadly echoed our ITS analysis, with most conditions showing level and slope changes close to the null. For three conditions, our CITS analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and MDD `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")` all showing sustained declines. All three of these symptoms had relatively large slope changes in our ITS analysis. In addition, the CITS level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "level")`, a decrease double in magnitude compared to the majority of estimates for other symptoms.

```{r figure_cits_outputs, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7, fig.height = 8, fig.align='center', out.width = '95%', fig.scap="Controlled interrupted time series effect estimates on Google Search density by symptom.", out.extra='',  fig.cap="\\label{figure_cits_outputs}Controlled interrupted time series effect estimates (A: slope change per 10 days and B: level shift)  on Google Search density by symptom. Effect estimates are represented as thick, horizontal lines in between colored bands, which represent the 99\\% confidence intervals for the estimates. Colors reflect the sign and magnitude of effect estimates. Dark blue values above zero indicate an increase in search density, while the yellow and green negative values indicate a decrease. The dotted horizontal line depicts a null effect. ADHD: Attention deficit hyperactivity disorder. CoC: clouding of consciousness. GAD: Generalized anxiety disorder. MDD: Major depressive disorder."}

model_outputs_main %>% 
  filter(disease %in% list_mental_health_symptoms) %>%
  function_model_main("exclude") %>%
  function_clean_diseases () %>%
  arrange(disease) %>%
  mutate(estimate = ifelse(coefficient == "post:time:trt", estimate*10, estimate),
         lower_99 = ifelse(coefficient == "post:time:trt", lower_99*10, lower_99),
         upper_99 = ifelse(coefficient == "post:time:trt", upper_99*10, upper_99)
  ) %>%
  mutate(coefficient = ifelse(coefficient == "post:time:trt", "A: slope change (per 10 days)",
                              ifelse(coefficient == "post:trt", "B: level shift", "ERROR"))) %>%
  mutate(sign = ifelse(estimate >0, TRUE, FALSE)) %>%

In both our analyses, search trends for anxiety, depression, and MDD showed potential immediate and sustained declines in density following November 16th. Search density for these three symptoms and the comparison search data for headaches is plotted in Figures \ref{figures_cits_data_anxiety} through \ref{figures_cits_data_mdd} at the level of U.S. states, U.S. counties, and international data. We observed relatively strong concordance between our CITS estimates and the observed trends in the data, with strong fit to both mental health symptoms and headaches. We further observed strong within-week patterns in searches, supporting our inclusion of fixed effects to account for this weekly periodicity.

```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time. In each row, search density data for two symptoms are displayed: anxiety in blue and headaches in grey. In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state. In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots. In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown. Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis. The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects). US: United States."}

function_figures_cits_data(geography = geography, "anxiety")

```
```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time. In each row, search density data for two symptoms are displayed: depression in blue and headaches in grey. In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state. In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots. In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown. Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis. The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects). US: United States."}

function_figures_cits_data(geography = geography, "depression")
